---
title: |
  
author: 
- Clovis Deletre
- Charles Vitry
date:
output:
  rmarkdown::html_document:
    theme: cerulean
    number_sections: no
    toc: yes
    toc_depth: 5
    toc_float: true
---
<style type="text/css">

body{ /* Normal  */
      font-size: 20px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 55px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 38px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 28px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 35px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

```{r setup, include=FALSE}


#install for export in pdf file
#tinytex::install_tinytex()
```
<br> </br>

```{r include=FALSE}
if(!require(forecast)) install.packages("tm", repos = "http://cran.us.r-project.org")
require(forecast)



library(ggplot2)

```



Import de la base, on select que la colonne des valeurs
```{r}
data <- read.csv("Trafic-voyageurs.csv", sep=";")

```


```{r}

```

```{r}


```

```{r}


```

```{r}


```

```{r}


```

```{r}


```

```{r}


```



